The pollination trade-off

### 2018-11-25 paper/manuscript.Rmd
Add numbers to words function

When examining the pollen deposited on stigmas of a species in a community we found that in a majority of cases either there was no significant relationship between heterospecific and conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)a). 
Although the overall relationship between between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was equal to those with a negative relationship (`r if(equal_pos_neg) {counts_facilitation_slope$nn[1]} else {stop("unequal")}`, `r counts_facilitation_slope$np[3]`%). 
This large variation among species was accompained by moderate variation within species (for those sampled in multiple communities). 
Indeed, `r nrow(sp_both_pos_neg)` species  (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed significantly positive relationships in some communities and negative in others. 
Furthermore, although neither a positive or negative was dominant, we found that, in almost all cases, more conspecific than heterospecific pollen was deposited on stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).

>>>>

When examining the pollen deposited on stigmas of a species in a community we found that in a majority of cases either there was no significant relationship between heterospecific and conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)a). 
Although the overall relationship between between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was equal to those with a negative relationship (`r if(equal_pos_neg) {counts_facilitation_slope$nn[1]} else {stop("unequal")}`, `r counts_facilitation_slope$np[3]`%). 
This large variation among species was accompained by moderate variation within species (for those sampled in multiple communities). 
Indeed, `r numbers2words(nrow(sp_both_pos_neg))` species  (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed significantly positive relationships in some communities and negative in others. 
Furthermore, although neither a positive or negative relationship was dominant, we found that, in almost all cases, more conspecific than heterospecific pollen was deposited on stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
